From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/acl2020_main.tex
[ACL2020] small things

% To streamline frequently used terms:
\newcommand{\langvis}{language\ \&\ vision\xspace}
\newcommand{\lv}{L\&V\xspace}
\newcommand{\mn}{ManyNames\xspace}
\newcommand{\vg}{VisualGenome\xspace}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\sameobject}{SameObject\xspace}
\newcommand{\cluster}{Cluster\xspace}

@@

% Terms that need to be replaced throughout the paper by more appropriate ones:
\newcommand{\arbitrary}{arbitrary$\rightarrow$?\xspace}
\newcommand{\categories}{classes\xspace}
\newcommand{\category}{class\xspace}

@@

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have investigated instance-level entry-level naming of objects in images.
To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
as opposed to previous works that mostly adopted a strictly taxonomic view of naming.
For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then finetune via transfer learning to entry-level names. 
In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling). 
%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%Future work will need to address these challenges.

>>>>

% To streamline frequently used terms:
\newcommand{\langvis}{language\ \&\ vision\xspace}
\newcommand{\lv}{L\&V\xspace}
\newcommand{\mn}{ManyNames\xspace}
\newcommand{\mnshort}{MN\xspace}
\newcommand{\vg}{VisualGenome\xspace}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\sameobject}{SameObject\xspace}
\newcommand{\cluster}{Cluster\xspace}

@@

% Terms that need to be replaced throughout the paper by more appropriate ones:
\newcommand{\arbitrary}{arbitrary\xspace}
\newcommand{\categories}{classes\xspace}
\newcommand{\category}{class\xspace}

@@

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have investigated instance-level entry-level naming of objects in images.
To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
as opposed to previous works that mostly adopted a strictly taxonomic view of naming.
For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then fine-tune via transfer learning to entry-level names. 
In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling). 
%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%Future work will need to address these challenges.

### 2019-12-10 papers/ACL2020/analysis.tex
[ACL2020] small things

%This might be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names . 
\iffalse
\cs{remove next couple of sentences? it's very assumptive}
This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts. 
\fi
%
None of the models predicted an inadequate name that was a linguistic, or any other error \sz{what??? no errors no more :-)}. 
Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on the \mn data reveals the problem of modeling a phenomenon of human behavior---object naming in our case---by leveraging data that only approximates the real-world situation in which the phenomenon occurs. \sz{this sounds a bit ... convoluted}

>>>>

%This might be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names . 
\iffalse
\cs{remove next couple of sentences? it's very assumptive}
This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts. 
\fi
%
None of the models predicted an inadequate name that was a linguistic, or any other error. 
Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on MN illustrates the challenges involved in collecting object names from image data to model natural object naming, and the relevance of thorough verification and quality control as we did in our work.

### 2019-12-10 papers/ACL2020/experiments.tex
[ACL2020] small things

Given the entry-level naming data from ManyNames which extends the \arbitrary naming data from \vg, we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.
The modeling experiments will assess these various modeling decisions for the task of entry-level naming, but using accuracy as a standard evaluation metric,
Section~\ref{sec:analysis} will analyse these results with respect to more detailed error types.
% found in the verification data in Section \ref{sec:verification}.
%We leave modeling experiments that take into account other possible names of objects for future work.

@@

\begin{itemize}
\item FRCNN$_{\text{VG1600}}$-VGMN:  This models extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.}. We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).  For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} The model uses the VGMN vocabulary (overlap of ManyNames and VG vocab).
\item ResNet-VGMN: For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{+++}.
Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names. The model uses the VGMN vocabulary.  The model is optimized on VG and MN ground truth names respectively.
 \item  ResNet-MN442:  The same model as before, but trained with a vocab of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
\end{itemize}

@@

		ResNet$_{\text{MN442}}$ & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
		ResNet$_{\text{VGMN}}$  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
		%ResNet$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
		%ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
		ResNet$_{\text{MN442}}$ & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
		\bottomrule
	\end{tabular}
	\caption{Model accuracy (in \%) on the \mn test objects. Vocab denotes the dataset used to induce the target vocabulary for training (the numbers give the size of the vocabulary). GTtrain gives the dataset that provides the ground truth labels during training, and VG and MN for testing \label{tab:exp_VGvsMN}.}
\end{table}
\fi
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc@{~}}
		\toprule
		&  & \multicolumn{2}{c}{GTtest} \\
		Model$_{\text{Vocab}}$ &  GTtrain &  VG & MN  \\ 
		\midrule
		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 \\
		\midrule \midrule
		\multicolumn{4}{c}{Classifiers: Transfer learning on MN}\\
		Features$_{\text{Vocab}}$ &   \\
		\midrule 
		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6  \\ 
		\midrule
		%ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\

		ResNet$_{\text{MN442}}$ & MN &            61.7 &              69.6  \\
		ResNet$_{\text{VGMN}}$  &   VG &  62.4 &              62.9  \\
		%ResNet$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
		%ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
		ResNet$_{\text{MN442}}$ & VG  &            63.7 &              63.7   \\
		\bottomrule
	\end{tabular}
	\caption{Model accuracy (in \%) on the \mn test objects. Vocab denotes the dataset used to induce the target vocabulary for training (the numbers are vocabulary size). GTtrain gives the dataset providing the ground truth labels for training, and GTtest for testing \label{tab:exp_VGvsMN}.}
\end{table}

%\paragraph{Measures}

@@

% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.  
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
%\cs{Left as items for the sake of a better overview for now}

>>>>

Given the entry-level naming data from \mn which extends the \arbitrary naming data from VisualGenome (VG), we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.
The modeling experiments will assess these various modeling decisions for the task of entry-level naming, but using accuracy as a standard evaluation metric,
Section~\ref{sec:analysis} will analyse these results with respect to more detailed error types.
% found in the verification data in Section \ref{sec:verification}.
%We leave modeling experiments that take into account other possible names of objects for future work.

@@

\begin{itemize}
\item FRCNN$_{\text{VG1600}}$-VGMN:  This models extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.}. We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).  For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer. The model uses the VGMN vocabulary (overlap of ManyNames and VG vocab).
\item ResNet-VGMN: For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{+++}.
Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names. The model uses the VGMN vocabulary.  The model is optimized on VG and MN ground truth names respectively.
 \item  ResNet-MN442:  The same model as before, but trained with a vocab of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
\end{itemize}

@@

		ResNet$_{\text{MN442}}$ & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
		ResNet$_{\text{VGMN}}$  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
		%ResNet$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
		%ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
		ResNet$_{\text{MN442}}$ & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
		\bottomrule
	\end{tabular}
	\caption{Model accuracy (in \%) on the \mn test objects. Vocab denotes the dataset used to induce the target vocabulary for training (the numbers give the size of the vocabulary). GTtrain gives the dataset that provides the ground truth labels during training, and VG and MN for testing \label{tab:exp_VGvsMN}.}
\end{table}
\fi
%\paragraph{Measures}

@@

% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.  
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
%\cs{Left as items for the sake of a better overview for now}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc@{~}}
		\toprule
		&  & \multicolumn{2}{c}{GTtest} \\
		Model$_{\text{Vocab}}$ &  GTtrain &  VG & MN  \\ 
		\midrule
		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 \\
		\midrule \midrule
		\multicolumn{4}{c}{Classifiers: Transfer learning on MN}\\
		Features$_{\text{Vocab}}$ &   \\
		\midrule 
		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6  \\ 
		\midrule
		%ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\

		ResNet$_{\text{MN442}}$ & MN &            61.7 &              69.6  \\
		ResNet$_{\text{VGMN}}$  &   VG &  62.4 &              62.9  \\
		%ResNet$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
		%ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
		ResNet$_{\text{MN442}}$ & VG  &            63.7 &              63.7   \\
		\bottomrule
	\end{tabular}
	\caption{Model accuracy (in \%) on the \mn test objects. Vocab denotes the dataset used to induce the target vocabulary for training (the numbers are vocabulary size). GTtrain gives the dataset providing the ground truth labels for training, and GTtest for testing \label{tab:exp_VGvsMN}.}
	\vspace{0ex}
\end{table}
